Multi-target detection with application to cryo-electron microscopy

### 2019-02-26 inverse_problems/inverse_problems.tex
Exp 3

\begin{figure}[h]
	\centering
	\includegraphics[width=.8\linewidth]{Einstein_recovery_error}
	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)). Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image. This does not require particle picking. A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly. Estimates are obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels from left to right) of size $4096\times 4096$, each containing $700$ image occurrences on average.}	
	%	\vspace{-8pt} 
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{Einstien_progress_examples}
	\caption{\label{fig:Einst_example} Recovery of Einstein from observations at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)). Averaged autocorrelations of the data allow to estimate the power spectrum of the target image. This does not require particle picking. The RRR algorithm produces the estimates,  obtained from $2\times 10^2,2\times 10^3,2\times 10^4,2\times 10^5$ observations (growing across panels from left to right).}	
	%	\vspace{-8pt} 
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=.8\linewidth]{Einstein_recovery_error}
	\caption{\label{fig:error_per_micro}Relative error curve for Experiment 3 in Figure~\ref{fig:Einst_example}.}
\end{figure}
